resistanceModelNotesAndy

### 2015-07-30 resistanceModelNotesAndy.Rmd
notes

I haven't done 20% better trees yet. Should I ?

@@

1. choose 1 tree to present to Ian & maybe this should be the most useful applied one ?
(which might be mix2 at 20% & 50% resistance)

1. redo the word results doc

>>>>

I haven't done 20% better trees yet. Should I ?
done now

** 23/7/15 **
prettifying trees
changed response from 0/1 to mixture/sequence

seems that it may have made the trees bigger, ARSE.

is it to do with pruning ?

tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]

** 30/7/15 **

checking on trees, and why they seem to change when I tweak formatting options
add a check into sensiAnPaper1All.Rmd

The tree is the same at the top (if reversed) but has more branches when 0/1 was changed to sequence/mixture.

treeResponse <- "betterMix2Seq_cP0.5"

tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
#[1] 0.01

What was this error before I made the conversion to text ?

I tried converting back to numeric and I got the same big tree ...

but the value of the error is lightly different :
tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"]
[1] 0.01072961

This is what the cptable looks like for the numeric version
numeric
> tree$cptable
          CP nsplit rel error    xerror       xstd
1 0.34549356      0 1.0000000 1.0000000 0.03385148
2 0.12875536      1 0.6545064 0.8047210 0.03285260
3 0.05150215      2 0.5257511 0.6931330 0.03173289
4 0.04184549      3 0.4742489 0.5107296 0.02889882
5 0.01824034      5 0.3905579 0.4527897 0.02768814
6 0.01287554      7 0.3540773 0.4163090 0.02683382
7 0.01180258      8 0.3412017 0.4098712 0.02667504
8 0.01072961     12 0.2939914 0.4012876 0.02645941
9 0.01000000     13 0.2832618 0.4098712 0.02667504

mixture/sequence
> tree$cptable
          CP nsplit rel error    xerror       xstd
1 0.34549356      0 1.0000000 1.0000000 0.03385148
2 0.12875536      1 0.6545064 0.7532189 0.03238844
3 0.05150215      2 0.5257511 0.6287554 0.03088571
4 0.04184549      3 0.4742489 0.4957082 0.02860113
5 0.01824034      5 0.3905579 0.4699571 0.02806478
6 0.01287554      7 0.3540773 0.4527897 0.02768814
7 0.01180258      8 0.3412017 0.4420601 0.02744467
8 0.01072961     12 0.2939914 0.4377682 0.02734549
9 0.01000000     13 0.2832618 0.4442060 0.02749387

Aha! when I repeat identical model, cptable is different 
> tree$cptable
          CP nsplit rel error    xerror       xstd
1 0.34549356      0 1.0000000 1.0000000 0.03385148
2 0.12875536      1 0.6545064 0.7618026 0.03247193
3 0.05150215      2 0.5257511 0.6351931 0.03097749
4 0.04184549      3 0.4742489 0.5085837 0.02885696
5 0.01824034      5 0.3905579 0.4635193 0.02792537
6 0.01287554      7 0.3540773 0.4248927 0.02704169
7 0.01180258      8 0.3412017 0.4163090 0.02683382
8 0.01072961     12 0.2939914 0.4098712 0.02667504
9 0.01000000     13 0.2832618 0.4098712 0.02667504

Can I get back to the nice smaller, neater tree ??

http://stackoverflow.com/questions/29197213/what-is-the-difference-between-rel-error-and-x-error-in-a-rpart-decision-tree

A rule of thumb is to choose the lowest level where the rel_error + xstd < xerror.

http://stackoverflow.com/questions/15318409/how-to-prune-a-tree-in-r

This does that :

nsplit <- tree$cptable[ tree$cptable[,"rel error"] + tree$cptable[,"xstd"]  < tree$cptable[,"xerror"],"nsplit"][1]

@@

1. what is xerror in tree$cptable it seems to be not constant between analyses ??? It is the cross validation parameter.

1. compare sequence/mixture tree with 0/1 for 1 of the chosen trees

1. is using the optimal error the way that susannah has suggested a problem ?
